Analytic Doppler Imaging

### 2019-08-19 tex/ms.tex
better twospec

%
\begin{center}
    \begin{longtable}{cll}
    \caption{Notation used in this paper} 
    \label{tab:notation} \\
    %
    \toprule
    \multicolumn{1}{c}{\textbf{Symbol}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{c}{\textbf{Reference}} \\
    \toprule
    \endhead
    %
    \endfoot
    %
    \endlastfoot
    %
    $a_{lm}$    & spectral spherical harmonic coefficient               & Equation~(\ref{eq:deconv:Ixi0})\\
    $\alm$      & vector of spectral spherical harmonic coefficients    & Equation~(\ref{eq:deconv:alm})\\
    $\bvec{a_0}$& $\alm$ at reference time $t = t_0$                    & Equation~(\ref{eq:deconv:R})\\
    $c$         & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
    $\Curve$    & curve of constant radial velocity                     & Equation~(\ref{eq:deconv:kT})\\
    $\Dargs$    & parameters of the Doppler field                       & \S\ref{sec:the_problem}\\
    $\D$        & logarithmic Doppler shift                             & Equation~(\ref{eq:the_problem:D})\\
    $F$         & flux                                                  & Equation~(\ref{eq:the_problem:F})\\
    $i$         & inclination                                           & Equation~(\ref{eq:kT:beta})\\
    $I$         & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
    $l$         & spherical harmonic degree                             & \\
    $m$         & spherical harmonic order                              & \\
    $\bvec{R}$  & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
    $\Surf$     & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
    $t$         & time                                                  & \S\ref{sec:the_problem}\\
    $\x$        & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
    $y_{lm}$    & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
    $Y_{lm}$    & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
    %
    %
    $\beta$     & relativistic parameter                                & Equation~(\ref{eq:the_problem:D})\\
    $\delta$    & Dirac delta function                                  & Equation~(\ref{eq:deconv:convolution})\\
    $\kT$       & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
    $\lambda$   & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
    $\lnlam$    & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
    $\lnlam_0$  & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\
    $\ylmbasis$ & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\
    $\omega$    & angular velocity                                      & Equation~(\ref{eq:kT:beta})\\
    %
    %
    $*$         & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
    $\circ$     & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})
\end{longtable}
\end{center}

@@

Given this new equation, we must change how we approach the inverse problem
(\S\ref{sec:inverse}). When solving for the spectrum given the spherical 
harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
and 
$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ 
in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
However, when solving for the spherical harmonic vector given the spectrum
(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
vector of interest appears in both the numerator and the denominator:
%
\begin{align}
    \label{eq:norm:fy}
    \bvec{f}
    &=
    \frac{
        \bvec{D}
        \,
        \bvec{S}
        \,
        \bvec{y}
    }{
        \bvec{B}
        \,
        \bvec{y}
    }
    \quad.
\end{align}
%
While we can solve for $\bvec{y}$ using a non-linear optimizer, it is
often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
to unity; i.e., the total flux from the star typically varies by only a
few percent. When this is the case, it is straightforward to linearize
this equation.
Following the notation from \S\ref{sec:solve_y}, we may therefore write
%
\begin{align}
    \bvec{f}
    &=
    \frac{
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    }{
        \bvec{B_0}
        \,
        +
        \bvec{B_1}
        \,
        \bvec{y_1}
    }
    \quad,
\end{align}
%
where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
and $\bvec{B}_\bvec{1}$ denotes the
matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
Expanding the expression above about 
$\bvec{B_1} \bvec{y_1} = \bvec{0}$, we have
%
\begin{align}
    \label{eq:norm:fapprox}
    \bvec{f}
    &\approx
    \left(
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    \right)
    \circ
    \left(
        \bvec{1}
        \,
        -
        \bvec{B_1}
        \,
        \bvec{y_1}
    \right)
    \nonumber \\
    &=
    \left(
        \bvec{D}\bvec{S_1}
        \,
        -
        \bvec{C}
    \right)
    \bvec{y_1}
    \,
    +
    \,
    \bvec{D} \, \bvec{s_0}
    \quad,
\end{align}
%
where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
constructed by multiplying the $i^\mathrm{th}$ row of $\bvec{B_1}$ by the
$i^\mathrm{th}$ element of $\bvec{D}\bvec{s_0}$.
%
This equation is now
linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
as before:
%
\begin{align}
    \label{eq:norm:yhat}
    \bvec{\hat{y}_1} &= 
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        (\bvec{f} - \bvec{D}\bvec{s_0})
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:norm:ycov}
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} &= 
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
Note, importantly, that these equations are valid only in the limit that the
change in the total flux from the star is small. Nevertheless, even in the 
general case, we find that solving this linear problem yields a good
starting point for a non-linear optimization, which we revisit in more
detail below.

@@

% Bibliography
\bibliography{bib}

>>>>

@@

Given this new equation, we must change how we approach the inverse problem
(\S\ref{sec:inverse}). When solving for the spectrum given the spherical 
harmonic vector (\S\ref{sec:solve_s}), we need only make the replacements
$\bvec{f} \rightarrow \nicefrac{\bvec{f}}{\bvec{B}\, \bvec{y}}$
and 
$\boldsymbol{\Sigma}_\mathbf{f} \rightarrow \nicefrac{\boldsymbol{\Sigma}_\mathbf{f}}{(\bvec{B}\, \bvec{y})^2}$ 
in Equations~(\ref{eq:inverse:shat}) and (\ref{eq:inverse:scov}).
However, when solving for the spherical harmonic vector given the spectrum
(\ref{sec:solve_y}), the problem is no longer linear in $\bvec{y}$, as the
vector of interest appears in both the numerator and the denominator:
%
\begin{align}
    \label{eq:norm:fy}
    \bvec{f}
    &=
    \frac{
        \bvec{D}
        \,
        \bvec{S}
        \,
        \bvec{y}
    }{
        \bvec{B}
        \,
        \bvec{y}
    }
    \quad.
\end{align}
%
While we can solve for $\bvec{y}$ using a non-linear optimizer, it is
often the case that the denominator in Equation~(\ref{eq:norm:fy}) is close
to unity; i.e., the total flux from the star typically varies by only a
few percent. When this is the case, it is straightforward to linearize
this equation.
Following the notation from \S\ref{sec:solve_y}, we may therefore write
%
\begin{align}
    \bvec{f}
    &=
    \frac{
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    }{
        \bvec{B_0}
        \,
        +
        \bvec{B_1}
        \,
        \bvec{y_1}
    }
    \quad,
\end{align}
%
where $\bvec{B_0} = \bvec{1}$ is the first column of $\bvec{B}$
and $\bvec{B}_\bvec{1}$ denotes the
matrix composed from the remaining $N - 1$ columns of $\bvec{B}$.
Expanding the expression above about 
$\bvec{B_1} \bvec{y_1} = \bvec{0}$ and keeping only terms up to
first order, we have
%
\begin{align}
    \label{eq:norm:fapprox}
    \bvec{f}
    &\approx
    \left(
        \bvec{D} \, \bvec{s_0}
        \,
        + 
        \,
        \bvec{D}\bvec{S_1}
        \,
        \bvec{y_1}
    \right)
    \circ
    \left(
        \bvec{1}
        \,
        -
        \bvec{B_1}
        \,
        \bvec{y_1}
    \right)
    \nonumber \\
    &\approx
    \left(
        \bvec{D}\bvec{S_1}
        \,
        -
        \bvec{C}
    \right)
    \bvec{y_1}
    \,
    +
    \,
    \bvec{D} \, \bvec{s_0}
    \quad,
\end{align}
%
where $\circ$ denotes an elementwise product and $\bvec{C}$ is a matrix
constructed by multiplying each row of $\bvec{B_1}$ by the
corresponding element of $\bvec{D}\bvec{s_0}$.
%
This equation is now
linear in $\bvec{y}_\bvec{1}$, so we may solve the least-squares problem
as before:
%
\begin{align}
    \label{eq:norm:yhat}
    \bvec{\hat{y}_1} &= 
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1}
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        (\bvec{f} - \bvec{D}\bvec{s_0})
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_\bvec{1}}}^{-1} \boldsymbol{\mu}_{\mathbf{y}_\bvec{1}}
    \right)
    \quad,
\end{align}
%
with covariance
%
\begin{align}
    \label{eq:norm:ycov}
    \boldsymbol{\Sigma}_\mathbf{\hat{y}_1} &= 
    \left(
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)^\top
        {\boldsymbol{\Sigma}_\mathbf{f}}^{-1}
        \left(\bvec{D}\bvec{S_1} - \bvec{C}\right)
        +
        {\boldsymbol{\Lambda}_{\mathbf{y}_1}}^{-1}
    \right)^{-1}
    \quad.
\end{align}
%
Note, importantly, that these equations are valid only in the limit that the
change in the total flux from the star is small. Nevertheless, even in the 
general case, we find that solving this linear problem yields a good
starting point for a non-linear optimization, which we revisit in more
detail below.

@@

% Table
\clearpage
\begin{center}
    \begin{longtable}{cll}
    \caption{Notation used in this paper \xxx{mostly complete up to sec 5}} 
    \label{tab:notation} \\
    \toprule
    \multicolumn{1}{c}{\textbf{Symbol}} &
    \multicolumn{1}{c}{\textbf{Description}} &
    \multicolumn{1}{c}{\textbf{Reference}} \\
    \toprule
    \endhead
    \endfoot
    \endlastfoot
    $a_{lm}$                 & spectral spherical harmonic coefficient               & Equation~(\ref{eq:deconv:Ixi0})\\
    $\alm$                   & vector of spectral spherical harmonic coefficients    & Equation~(\ref{eq:deconv:alm})\\
    $\bvec{a_0}$             & $\alm$ at reference time $t = t_0$                    & Equation~(\ref{eq:deconv:R})\\
    $\bvec{A_0}$             & matrix form of $\bvec{a_0}$                           & Equation~(\ref{eq:inverse:azero})\\
    $c$                      & speed of light                                        & Equation~(\ref{eq:kT:beta})\\
    $\Curve$                 & curve of constant radial velocity                     & Equation~(\ref{eq:deconv:kT})\\
    $\Dargs$                 & parameters of the Doppler field                       & \S\ref{sec:the_problem}\\
    $\D$                     & logarithmic Doppler shift                             & Equation~(\ref{eq:the_problem:D})\\
    $\Doppler$               & Doppler design matrix                                 & Equation~(\ref{eq:linear:f})\\
    $\bvec{f}$               & vector of observed flux values                        & Equation~(\ref{eq:linear:f})\\
    $F$                      & flux                                                  & Equation~(\ref{eq:the_problem:F})\\
    $i$                      & inclination                                           & Equation~(\ref{eq:kT:beta})\\
    $I$                      & specific intensity                                    & Equation~(\ref{eq:the_problem:Ixi})\\
    $l$                      & spherical harmonic degree                             & \\
    $m$                      & spherical harmonic order                              & \\
    $\bvec{R}$               & Wigner rotation matrix                                & Equation~(\ref{eq:deconv:R})\\
    $\bvec{s}$               & vector representation of the spectrum                 & Equation~(\ref{eq:inverse:azero})\\
    $\Surf$                  & projected visible area of the star                    & Equation~(\ref{eq:the_problem:F})\\
    $t$                      & time                                                  & \S\ref{sec:the_problem}\\
    $\x$                     & Cartesian position on the sky                         & \S\ref{sec:the_problem}\\
    $y_{lm}$                 & spherical harmonic coefficient                        & \S\ref{sec:inverse}\\
    $\bvec{s}$               & vector of spherical harmonic coefficients             & Equation~(\ref{eq:inverse:azero})\\
    $Y_{lm}$                 & spherical harmonic                                    & Equation~(\ref{eq:deconv:Ixi0})\\
    $\beta$                  & relativistic parameter                                & Equation~(\ref{eq:the_problem:D})\\
    $\delta$                 & Dirac delta function                                  & Equation~(\ref{eq:deconv:convolution})\\
    $\kT$                    & convolution kernel basis vector                       & Equation~(\ref{eq:deconv:kT})\\
    $\lambda$                & wavelength (in nm)                                    & \S\ref{sec:the_problem}\\
    $\lnlam$                 & $\ln\lambda$ (observer frame)                         & \S\ref{sec:the_problem}\\
    $\lnlam_0$               & $\ln\lambda$ (rest frame)                             & \S\ref{sec:the_problem}\\
    $\boldsymbol{\Lambda}$   & prior covariance matrix                               & \\
    $\ylmbasis$              & spherical harmonic basis vector                       & Equation~(\ref{eq:deconv:ylmbasis})\\
    $\boldsymbol{\Sigma}$    & covariance matrix                                     & \\
    $\omega$                 & angular velocity                                      & Equation~(\ref{eq:kT:beta})\\
    $*$         & convolution                                           & Equation~(\ref{eq:deconv:convolution_def})\\
    $\circ$     & element-wise product                                  & Equation~(\ref{eq:norm:fapprox})
\end{longtable}
\end{center}

% Bibliography
\clearpage
\bibliography{bib}
